# My First knitr Document

## Introduction

### Basic

This is some text (i.e. a "text chunk")

### R Code Chunk

Here is a code chunk
```{r}
set.seed(1)
x <- rnorm(100)
mean(x)
```


### Values in Text

```{r computetime, echo=FALSE}
time <- format(Sys.time(), "%a %b %d %X %Y")
rand <- rnorm(1)
```

The current time is `r time`.  My favorite randome number is `r rand`

### Plotting

Let's first simulate some data
```{r simulatedata, echo=TRUE}
x <- rnorm(100); y <- x +rnorm(100, sd=0.5)
```

Here is a scatterplot of the data.
```{r scatterplot, fig.height=4}
par(mar=c(5,4,1,1), las = 1)
plot(x,y,main="My simluated data")
```

### Tables using xtable

```{r fitmodel}
library(datasets)

data(airquality)
fit <- lm(Ozone ~ Wind + Temp + Solar.R, data=airquality)
```

Here is a table of regression coefficients.

```{r showtable, results="asis"}
library(xtable)
xt <- xtable(summary(fit))
print(xt, type="html")
```

### Global Options

```
  '''{r setoptions, echo=FALSE}
  opts_chuck$set(echo = FALSE, results = "hide")
  ''' 
```

### Common Options  
  * Output  
      * `results`: `"asis"`, `"hide"`  
      * `echo`: `TRUE`, `FALSE`  
  * Figures  %>% 
      * `fig.height`: numeric  
      * `fig.widht`: numeric  
      
### Caching Computations  
  * `cache=TRUE` can be set on chunk by chunk basis  
  * After first run, results are cached
